Verifying Demonstrations

### 2017-08-21 properties.tex
Fixes warnings from Syntastic
Changes to use \mode to hide frames, fixes #10

\mode*
\section{The idea}
\label{TheIdea}

@@

\subsection{Verification}
\label{Verification}

@@

\begin{frame}<presentation>
  \begin{requirements}[V\ref*{EligibilityVerif}.]
  \item\label{CountOnce} Prove that no individual can be counted more than 
    once.
  \item\label{CreatedAfterStart} Prove that the data was created after the 
    start of the event.
  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
    of the event.
  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
    physical location of the event.
  \item\label{DesignatedEvent} Prove that the data is designated for the event.
\end{requirements}
\end{frame}

@@

\begin{frame}<presentation>
\begin{idea}[Temporal eligibility]
  \begin{itemize}
    \item There is a mechanism that provides the properties of a poset: a 
      blockchain.

    \item There are also other structures, e.g.\ a directed 
      graph~\cite{BlockchainFreeCryptocurrencies}.
  \end{itemize}
\end{idea}
\end{frame}

@@

\begin{frame}<presentation>
  \begin{idea}[Created before end]
    \begin{itemize}
      \item Submit the proof to storage.
      \item The proof must've been created before it was included (duh!).
    \end{itemize}
  \end{idea}
\end{frame}

@@

\begin{frame}<presentation>
  \begin{idea}[Created after start]
    \begin{itemize}
      \item Include an unpredictable value in the proof.
      \item This could be e.g.\ the hash of the \enquote{head} of the 
        \ac{tposet}.
      \item This prevents creating proofs for future protests.
    \end{itemize}
  \end{idea}
\end{frame}

@@

\begin{frame}<presentation>
  \begin{idea}[Spatial eligibility]
    \begin{itemize}
      \item Include \iac{LP} which is \enquote{witnessed} (signed) by other 
        participants.
      \item We have a coarse location, just within protest area.
      \item This allows protesters to move around to collect signatures.
      \item This provides privacy for the location, e.g.\ cannot map to 
        surveillance cameras.
    \end{itemize}
  \end{idea}
\end{frame}

@@

\begin{frame}<presentation>
  \begin{idea}[Count once]
    \begin{itemize}
      \item Any two proofs by the same individual are linkable.
      \item Includes signature made by a verified key.
    \end{itemize}
  \end{idea}

  \pause

  \begin{idea}[Designated event]
    \begin{itemize}
      \item Include a protest-specific identifier.
      \item E.g.\ hash of the \enquote{manifesto}.
    \end{itemize}
  \end{idea}
\end{frame}

@@

\begin{frame}<presentation>
  \begin{idea}[Individual verifiability]
    \begin{itemize}
      \item Proofs are stored publicly.
      \item Each participant can check that their proof is indeed included.
    \end{itemize}
  \end{idea}

  \pause

  \begin{idea}[Universal verifiability]
    \begin{itemize}
      \item Proofs are stored publicly.
      \item Anyone can download all proofs, verify eligibility and then count 
        them.
    \end{itemize}
  \end{idea}
\end{frame}

\subsection{Privacy}
\label{Privacy}

@@

In voting, we have the following requirements:
\begin{frame}
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
  individual vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\pause
\mode<presentation>{
  \begin{remark}
    P\ref{CoercionResistance} \(\implies\)
    P\ref{ReceiptFreeness} \(\implies\)
    P\ref{VotePrivacy}
  \end{remark}
}
\end{frame}
\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
\Cref{CoercionResistance} is probably not possible to achieve for protests:
e.g.\ Eve can simply physically bring Alice to a protest against her will.
This leaves us with \cref{ReceiptFreeness,VotePrivacy}.

\begin{frame}<presentation>
  \begin{remark}
    \begin{itemize}
      \item Coercion resistance is difficult to achieve for voting.
      \item It doesn't make much sense for protests.
      \item E.g.\ Eve physically brings Alice to a protest she doesn't want to 
        participate in.
      \item That leaves us with receipt freeness and vote privacy.
    \end{itemize}
  \end{remark}
\end{frame}

A demonstration is very different from voting in one sense: at a demonstration, 
Alice must be physically present and that very presence shows her support for 
the cause.
In voting, on the other hand, everyone is present and Alice has multiple 
options which are not revealed by her mere presence.
% XXX Check if unlinkable is the correct term
Hence, if Alice submits a proof of participation, the proof must be unlinkable 
to Alice, yet, if Alice submits another proof, those two proofs must be 
linkable (due to eligibility verification, \cref{EligibilityVerif}) so that 
Alice is not counted twice.
Receipt freeness implies that Alice enjoys deniability against Eve:
Eve should not be able to use the published proof to tie it to Alice, even if 
Eve has access to Alice's device (i.e.\ all her private keys).
I.e.\ Eve should not be able to reproduce the same proof.

\begin{frame}<presentation>
  \begin{remark}
    \begin{itemize}
      \item Voting: different alternatives when participating.
      \item Protesting: participation implies the alternative.
    \end{itemize}
  \end{remark}

  \pause

  \begin{idea}[Vote privacy]
    \begin{itemize}
      \item Eve shouldn't be able to link Alice's published proof back to 
        Alice.
      \item But if Alice publishes two proofs, those two are linkable.
      \item We're not interested in unmasking trolls, just not count them more 
        than once.
    \end{itemize}
  \end{idea}
\end{frame}

\begin{frame}<presentation>
  \begin{idea}[Receipt freeness (deniability)]
    \begin{itemize}
      \item If Eve compromises Alice's device, she should not be able to use 
        it to verify that she participated.

@@

      \item But Alice should still not be able to participate twice.
    \end{itemize}
  \end{idea}
\end{frame}

>>>>

\mode*
\section{The idea}%
\label{TheIdea}

@@

\subsection{Verification}%
\label{Verification}

@@

\mode<presentation>{%
\begin{frame}
  \begin{requirements}[V\ref*{EligibilityVerif}.]
  \item\label{CountOnce} Prove that no individual can be counted more than 
    once.
  \item\label{CreatedAfterStart} Prove that the data was created after the 
    start of the event.
  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
    of the event.
  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
    physical location of the event.
  \item\label{DesignatedEvent} Prove that the data is designated for the event.
\end{requirements}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
\begin{idea}[Temporal eligibility]
  \begin{itemize}
    \item There is a mechanism that provides the properties of a poset: a 
      blockchain.

    \item There are also other structures, e.g.\ a directed 
      graph~\cite{BlockchainFreeCryptocurrencies}.
  \end{itemize}
\end{idea}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Created before end]
    \begin{itemize}
      \item Submit the proof to storage.
      \item The proof must've been created before it was included (duh!).
    \end{itemize}
  \end{idea}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Created after start]
    \begin{itemize}
      \item Include an unpredictable value in the proof.
      \item This could be e.g.\ the hash of the \enquote{head} of the 
        \ac{tposet}.
      \item This prevents creating proofs for future protests.
    \end{itemize}
  \end{idea}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Spatial eligibility]
    \begin{itemize}
      \item Include \iac{LP} which is \enquote{witnessed} (signed) by other 
        participants.
      \item We have a coarse location, just within protest area.
      \item This allows protesters to move around to collect signatures.
      \item This provides privacy for the location, e.g.\ cannot map to 
        surveillance cameras.
    \end{itemize}
  \end{idea}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Count once]
    \begin{itemize}
      \item Any two proofs by the same individual are linkable.
      \item Includes signature made by a verified key.
    \end{itemize}
  \end{idea}

  \pause{}

  \begin{idea}[Designated event]
    \begin{itemize}
      \item Include a protest-specific identifier.
      \item E.g.\ hash of the \enquote{manifesto}.
    \end{itemize}
  \end{idea}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Individual verifiability]
    \begin{itemize}
      \item Proofs are stored publicly.
      \item Each participant can check that their proof is indeed included.
    \end{itemize}
  \end{idea}

  \pause{}

  \begin{idea}[Universal verifiability]
    \begin{itemize}
      \item Proofs are stored publicly.
      \item Anyone can download all proofs, verify eligibility and then count 
        them.
    \end{itemize}
  \end{idea}
\end{frame}
}

\subsection{Privacy}%
\label{Privacy}

@@

In voting, we have the following requirements:
\begin{frame}
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
  individual vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\pause{}
\mode<presentation>{%
  \begin{remark}
    P\ref{CoercionResistance} \(\implies\)
    P\ref{ReceiptFreeness} \(\implies\)
    P\ref{VotePrivacy}
  \end{remark}
}
\end{frame}
\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
\Cref{CoercionResistance} is probably not possible to achieve for protests:
e.g.\ Eve can simply physically bring Alice to a protest against her will.
This leaves us with \cref{ReceiptFreeness,VotePrivacy}.

\mode<presentation>{%
\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item Coercion resistance is difficult to achieve for voting.
      \item It doesn't make much sense for protests.
      \item E.g.\ Eve physically brings Alice to a protest she doesn't want to 
        participate in.
      \item That leaves us with receipt freeness and vote privacy.
    \end{itemize}
  \end{remark}
\end{frame}
}

\subsubsection{Vote privacy}

A demonstration is very different from voting in one sense: at a demonstration, 
Alice must be physically present and that very presence shows her support for 
the cause.
In voting, on the other hand, everyone is present and Alice has multiple 
options which are not revealed by her mere presence.
% XXX Check if unlinkable is the correct term
Hence, if Alice submits a proof of participation, the proof must be unlinkable 
to Alice, yet, if Alice submits another proof, those two proofs must be 
linkable (due to eligibility verification, \cref{EligibilityVerif}) so that 
Alice is not counted twice.

\mode<presentation>{%
\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item Voting: different alternatives when participating.
      \item Protesting: participation implies the alternative.
    \end{itemize}
  \end{remark}

  \pause{}

  \begin{idea}[Vote privacy]
    \begin{itemize}
      \item Eve shouldn't be able to link Alice's published proof back to 
        Alice.
      \item But if Alice publishes two proofs, those two are linkable.
      \item We're not interested in unmasking trolls, just not count them more 
        than once.
    \end{itemize}
  \end{idea}
\end{frame}
}

\subsubsection{Receipt freeness}

Receipt freeness implies that Alice enjoys deniability against Eve:
Eve should not be able to use the published proof to tie it to Alice, even if 
Eve has access to Alice's device (i.e.\ all her private keys).
I.e.\ Eve should not be able to reproduce the same proof and thus verify that 
Alice has created one of the proofs.

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Receipt freeness (deniability)]
    \begin{itemize}
      \item If Eve compromises Alice's device, she should not be able to use 
        it to verify that she participated.

@@

      \item But Alice should still not be able to participate twice.
    \end{itemize}
  \end{idea}
\end{frame}
}

\begin{frame}
  \begin{question}
    Will such a signature scheme solve both problems?
  \end{question}
  \begin{question}
    Is there such a signature scheme?
    Can we construct it?
  \end{question}
  \begin{question}
    What Alice submits her proof, stores the hash of the block, removes proof 
    and signature key?
  \end{question}
\end{frame}

\subsubsection{Architecture}

We also have an architectural problem.
If the system is only run by volunteering activists, then Eve can simply 
analyse network traffic to detect who is running nodes in the system.

\begin{frame}
  \begin{question}
    Shall we offer a platform that is run by a variety of institutions who 
    offers to verify protests?
    Or go strictly peer-to-peer?
  \end{question}
  \begin{question}
    If strictly peer-to-peer, and only run by protesters, one can infer that 
    they are protesters by running such a node.
    Can this be mitigated?
  \end{question}
\end{frame}

We would still have the problem of how protesters submit their proofs to the 
system.
This must be done anonymously.

\begin{frame}
  \begin{question}
    How do we submit the proofs to storage?
    Voting normally uses mix-nets.
    Submit over Tor~\cite{Tor}?
  \end{question}

  \begin{remark}
    Without anonymous submission we don't get vote privacy, thus no receipt 
    freeness either.
  \end{remark}
\end{frame}
